Osa

### 2021-09-10 article/article.Rmd
fixed underlying data toggle in fig function

---
title: "Osa"
output: 
  html_notebook: 
    toc: yes
    code_folding: hide
    theme: spacelab
    fig_caption: yes
bibliography: references.bib
---

@@

-   Tropical forests store most terrestrial biomass @pan2013 and biodiversity (CITE, but are losing functions, especially in the neotropics @hubau2020, as most tropical forests become secondary (\@FAO20.

@@

-   Neotropical secondary forests accumulate biomass \>10x faster than old-growth forests @poorter2016, and offset \~10% of carbon emissions from Amazonian deforestation @smith2020 .
-   They also recover taxonomic richness quite quickly, averaging 80% of old-growth forest levels in 20y @rozendaal2019 .
-   However, secondary neotropical forests diverge widely in taxonomic composition @norden2015 .

@@

Half of all forests lie half of a kilometer from an ecotone @haddad2015, suggesting that edge effects from adjacent habitats are widespread aspects of secondary forest regeneration.

-   Tropical forests lose 22% carbon along edges \>100m, in part due to shorter trees and less leaf mass @ordway2020 .

@@

@@

## Shade / Canopy

@@

    1.  shade x distance @ordway2020 + timber sp?

    2.  height @ordway2020

    3.  wood density @poorter2019

    4.  total biomass x dist @ordway2020 + timber sp?

@@

## Edge effects

@@

>>>>

---
title: "Osa"
output:
  html_document:
    toc: yes
    df_print: paged
  html_notebook:
    toc: yes
    code_folding: hide
    theme: spacelab
    fig_caption: yes
bibliography: references.bib
---

@@

-   Tropical forests store most terrestrial biomass ( @pan2013 ) and biodiversity (CITE, but are losing functions, especially in the neotropics ( @hubau2020 ), as most tropical forests become secondary (\@FAO20.

@@

-   Neotropical secondary forests accumulate biomass \>10x faster than old-growth forests ( @poorter2016 ), and offset \~10% of carbon emissions from Amazonian deforestation ( @smith2020 ).
-   They also recover taxonomic richness quite quickly, averaging 80% of old-growth forest levels in 20y ( @rozendaal2019 ).
-   However, secondary neotropical forests diverge widely in taxonomic composition ( @norden2015 ).

@@

Half of all forests lie half of a kilometer from an ecotone ( @haddad2015 ), suggesting that edge effects from adjacent habitats are widespread aspects of secondary forest regeneration.

-   Tropical forests lose 22% carbon along edges \>100m, in part due to shorter trees and less leaf mass ( @ordway2020 ).

@@

    -   supported by inference?!

@@

```{r setup, echo = F, message = F}
knitr::opts_chunk$set(
  echo = F,
  message = F,
  warning = F
)
library(here)
```

## Biomass

@@

    1.  shade x distance ( @ordway2020 ) + timber sp?

    2.  height ( @ordway2020 )

    3.  wood density ( @poorter2019 )

    4.  total biomass x dist ( @ordway2020 ) + timber sp?

@@

[RESULTS TEXT]

```{r fig1}
source(
  here(
    "figs/fig1.R"
  )
)
fig1
```

## Composition

@@

```{r fig2}

```
